---
title: "Practical_Machine_Learning_Project"
author: "Yves Ndjoli"
date: "Sunday, January 25, 2015"
output: html_document
---

This is my project from the courseras course Practical Machine Learning of the specialization Data Science.  

In this project we have to built a machine learning model with help of train datas to classify the test datas from accelerometers on the belt, forearm, arm, and dumbell of 6 participants.  

More information about the data avalaible here http://groupware.les.inf.puc-rio.br/har    

download and read the file  
```{r}
#vSourceTrain= "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
#vSourceTest= "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

#download.file(vSourceTrain, destfile="TrainData.csv")
#download.file(vSourceTest, destfile="TestData.csv")

trainfile="TrainData.csv"
testfile="TestData.csv"

TrainDataTemp1=read.csv(trainfile,na.strings=c("", "NA", "NULL"))
TestDataTemp1=read.csv(testfile,na.strings=c("", "NA", "NULL"))
```

# Exploring the datas

```{r, results="hide"}
head(TrainDataTemp1,5)
tail(TrainDataTemp1,5)
summary(TrainDataTemp1)
```

# Prepossing

Remove columns with NAs values
```{r}
TrainDataTemp2=TrainDataTemp1[,colSums(is.na(TrainDataTemp1)) < length(TrainDataTemp1)*3/4]
```

Remove columns which name contains X, timestamp, user_name, window
```{r}
TrainDataTemp3=TrainDataTemp2[,-c(1,2,3,4,5,6,7)]
dim(TrainDataTemp3)
```

Keep same columns for the test datas
```{r}
TestDataTemp2=TestDataTemp1[,setdiff(names(TrainDataTemp3), "classe")]
dim(TestDataTemp2)
```

# Partition of TrainData
```{r}
require(caret)
set.seed(1000)
inTrain=createDataPartition(y=TrainDataTemp3$classe,p=0.75,list=FALSE)
Ttraining=TrainDataTemp3[inTrain,]
Ttest=TrainDataTemp3[-inTrain,]
dim(Ttraining)
dim(Ttest)
```

# Fit a model and testing

Fit a model with tree method rpart
```{r}
fitModel=train(classe~.,data=Ttraining,method="rpart")
```

Prediction for the Ttest
```{r}
Ppred = predict(fitModel, Ttest)
```

Check the prediction
```{r}
confusionMatrix(Ppred, Ttest$classe)
```
Low accuracy: 0.51, that means height probability of miss predictions

Fit a model again now with the random forest method    
Don't use the caret package like rpart because performance problem  
```{r}
library(randomForest)
#fitModel2=train(classe~.,data=Ttraining,method="rf")
fitModel2= randomForest(classe ~. , data=Ttraining, method="class")
```

Prediction for the Ttest
```{r}
Ppred2 = predict(fitModel2, Ttest)
```

Check the prediction
```{r}
confusionMatrix(Ppred2, Ttest$classe)
```
Good accuracy 0.99, that means few predictions errors

Final testing with the test datas
```{r}
Ppred3 = predict(fitModel2, TestDataTemp2)
Ppred3
```

